Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-08 inc/photocathode/single_photon/single_photon.tex
include a note on relative yield
Began to split out 2PTE from ESTE section
tweaks to single_photon section

Single-photon photoemission is the most common photoemission process and the easiest to explain.
As described by Einstein in his famous paper on ``the photoelectric effect'' \cite{einstein_uber_1905}, as it is colloquially known, if an electron absorbs a photon whose energy is sufficient to promote the electron above the local vacuum level, it become free to leave the host material.

@@

An example of single-photon photoemission is presented in \ref{fig:single_photon_tungsten}, wherein a sample of polished tungsten (W), having a work function $\Phi \approx $ 4.3-4.5 eV \cite{yen_thermally_1980}, is used as a photocathode.
When paired with our $\hbar \omega = $ 4.75 eV photon energy laser (see Section \ref{sec:laser}) the excess photoemission energy $\Delta E = \hbar \omega - \Phi \approx $ 0.2 eV.
The linear dependence of the electron yield (circles) on the laser pulse energy is indicative of a single photon process, as expected.
The fact that the Fourier plane spot-size, directly related the initial transverse momentum variance $\Delta p_{\smallT}$, is unchanged over the full range of laser power is also expected, since by $\Delta p_{\smallT} = \sqrt{ m \Delta E / 3 } $ \cite{dowell_quantum_2009}, $\Delta p_{\smallT}$ only depends on $\Delta E$.

>>>>

Single-photon photoemission is the most common photoemission process and the easiest to explain.
As described by Einstein in his famous paper on ``the photoelectric effect'' \cite{einstein_uber_1905}, as it is colloquially known, if an electron absorbs a photon whose energy is sufficient to promote the electron above the local vacuum level, it become free to leave the host material.
The material dependent minimum energy needed to eject an electron is termed its ``work function'' $\Phi$.
Any additional energy above the work function remains with the ejected electron, usually in the form of kinetic energy, and is called the ``excess photoemission energy.''

@@

An example of single-photon photoemission is presented in \ref{fig:single_photon_tungsten}, wherein a sample of polished tungsten (W), having a work function $\Phi \approx $ 4.3-4.5 eV \cite{yen_thermally_1980}, is used as a photocathode.
When paired with our $\hbar \omega = $ 4.75 eV photon energy laser (see Section \ref{sec:laser}) the excess photoemission energy $\Delta E = \hbar \omega - \Phi \approx $ 0.35 eV.
The linear dependence of the electron yield (circles) on the laser pulse energy is indicative of a single photon process, as expected since each absorbed photon may eject one electron.
In this experiment, the yield is determined by integrating the total counts recorded on the CCD detector and therefore is only a relative measurement.
The fact that the Fourier plane spot-size (squares), directly related the initial transverse momentum variance $\Delta p_{\smallT}$, is unchanged over the full range of laser power is also expected, since by $\Delta p_{\smallT} = \sqrt{ m \Delta E / 3 } $ \cite{dowell_quantum_2009}, $\Delta p_{\smallT}$ only depends on $\Delta E$.
